---
title: "Overview of farsr"
author: "Slava Kohut"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.align = 'center',
  comment = "#>"
)

devtools::load_all('/home/stanley/coursera/2018-r-packages/farsr/')
```

# Introduction

The goal of  __farsr__ is to provide a set of tools for working with
the Fatality Analysis Reporting System (FARS) data. 
There are five functions that come with the package:

1. _make\_filename_
2. _fars\_read_
3. _fars\_read\_years_
4. _fars\_summarize\_years_ 
5. _fars\_map\_state_

# Functions 

_make\_filename_ generates a standard filename using a year:
```{r}
make_filename(2013)
```

_fars\_read_ is the basic function for reading data sets. An error will be raised if the input file does not exist.
```{r}
setwd('../raw-data')
fars_read(make_filename(2013))
```

_fars\_read\_years_ is a wrapper around _fars\_read_ and _make\_filename_ for reading multiple files in a list.

_fars\_read\_years_ uses some _dplyr_ functions to generate a summary (by-month counts) of accidents for a data set for a given year: 
```{r}
setwd('../raw-data')
fars_summarize_years(2013:2014)
```

_fars\_map\_state_ projects all accidents for an input state and year on a state polygon.
The code below generates a map for California 2015 data.
```{r, fig.width=8, fig.height=8}
setwd('../raw-data')
fars_map_state(6,2015)
```
